Testing atlantisom: true biomass output from Atlantis

### 2019-05-21 Atlantisom2SSworkflowtest.Rmd
combine blocks save lf

@@

```{r savelengths}
#save for later use, takes a long time to generate
saveRDS(length_census_ss, file.path(d.name, paste0(scenario.name, "length_census_sardhakeboca.rds")))
```

>>>>

#save for later use, takes a long time to generate
saveRDS(length_census_ss, file.path(d.name, paste0(scenario.name, "length_census_sardhakeboca.rds")))

@@
